\documentclass[../main]{subfiles}
\begin{document}

%Yohan

\chapter{A Category of Fractions}
\label{sec:p3c14}
We recall that our general object in these sections is to answer the following question. Suppose given  $E_{\ast}(X)$ and $E_{\ast}(Y)$. What can we say about $\left[ X,Y \right]_{\ast}$?

Now it is clear that we cannot say everything. For example, suppose $E = HZ_{2}$; given $(HZ_{2})_{\ast}(X)$ and $(HZ_{2})_{\ast}(Y)$ there is no hope of finding out anything about the old torsion in $\left[ X,Y \right] _{\ast}$. 

More generally, we will say that a morphism $f\colon X \to X^{\prime} $ is an E-equivalent if the induced homomorphism 
$$
  f\colon E_{\ast}(X) \to E_{\ast}(X^{\prime}) 
$$
is an isomorphism. This can happen without $f$ being an equivalence; for example, take $E = HZ _{2}$, $X = HZ_3$, $X^{\prime}= pt.$ Then it is clear that methods based on E-cohomology cannot tell $X$ and $X^{\prime}$ apart.\\
It therefore seems best to introduce a new category in which one does not attempt to tell $X$ and $X^{\prime}$ apart. In technical terms I have to start from the stable category and define a category of fractions.\\
(Added later.) I owe to A.K. Bousfield the remark that the procedure below involves very serious set-theoretical difficulties. Therefore it will be best to interpret this section not as a set of theorems, but as a programme, that is, as a guide to what one might wish to prove.\\
Let $C$ be the stable category already constructed.
\begin{theorem} \label{thm:p3ch14.1}
There exists a category $F$, called the category of fractions, and a functor
$$
  T\colon C \to F 
$$ with the following properties.

\begin{enumerate} 
  \item [(i)] if $e\colon X \to Y $ is an E-equivalence in $C$, then  $\te{T}(e)$ is an actual equivalence in F, i.e., it has an inverse  $\te{T}(e)^{-1}$.
  \item [(ii)] T is an universal with respect this property; given a category $C$ and a functor $U\colon C \to G$ such that $e$ an E-equivalence implies  $\te{U}(e)$ is an equivalence in $G$, then there exists one and only functor  $V\colon F \to G  $ such that $U = VT$. 
\[\begin{tikzcd}
	C &&&& G \\
	\\
	\\
	\\
	&&&& F
	\arrow["T", from=1-1, to=1-5]
	\arrow["U"', from=1-1, to=5-5]
	\arrow["V", dashed, from=1-5, to=5-5]
\end{tikzcd}\]
\item [iii] The objects of $F$ are the same as the objects of $C$, and  $T$ is the identity on objects.
\item [iv] Every morphism in $F$ from $X$ to  $Y$ can be written  $\te{T}(e)^{-1}\te{T}(f)$, where $f\colon X \to Y^{\prime}  $ and $f\colon Y \to Y^{\prime}  $ are in $C$ and  $e$ is an E-equivalence. \\
  \[\begin{tikzcd}
	&&&& {Y'} \\
	\\
	\\
	X &&&& Y
	\arrow["f", from=4-1, to=1-5]
	\arrow["e"', from=4-5, to=1-5]
\end{tikzcd}\]
We have $\te{T}(e_1)^{-1}\te{\te{T}}(f_1)=\te{T}(e_2)^{-1}\te{T}(f_2)$ in $F$ if and only if there exists a diagram of the following form in $C$. 

\[\begin{tikzcd}
	&&&&& {Y_1} \\
	X &&&& Y && {Y'} \\
	&&&&& {Y_2}
	\arrow["{f_1}", from=2-1, to=1-6]
	\arrow["{f_2}"', from=2-1, to=3-6]
	\arrow["{e_1}"', from=2-5, to=1-6]
	\arrow["{e'_1}"', from=1-6, to=2-7]
	\arrow["{e'_2}"{description}, from=3-6, to=2-7]
	\arrow["{e_2}"{description}, from=2-5, to=3-6]
\end{tikzcd}\]
\item [(v)] Every morphism in $F$ from $X$ to $Y$ can be written  $\te{T}(f)\te{T}(e)^{-1}$, where $f\colon X^{\prime} \to Y  $ and $e\colon X^{\prime} \to X  $ are in $C$ and  $e$ is an E-equivalence.
\[\begin{tikzcd}
	&& X \\
	&&&& Y \\
	{X'}
	\arrow["e", from=3-1, to=1-3]
	\arrow["f"', from=3-1, to=2-5]
\end{tikzcd}\]
\end{enumerate}
\end{theorem}
We have $\te{T}(f_1)\te{T}(e_1)^{-1} =\te{T}(f_2)\te{T}(e_2)^{-1}$ in $F$ if and only if there exists a diagram of the following form in $C$. 
\[\begin{tikzcd}
	&& {X_1} \\
	{X'} &&&& X &&& Y \\
	&& {X_2}
	\arrow["{e'_1}"', from=2-1, to=1-3]
	\arrow["{e'_2}"', from=2-1, to=3-3]
	\arrow["{e_1}"', from=1-3, to=2-5]
	\arrow["{e_2}"{description}, from=3-3, to=2-5]
	\arrow["{f_1}"{description}, from=1-3, to=2-8]
	\arrow["{f_2}"{description}, from=3-3, to=2-8]
\end{tikzcd}\]
If one takes only parts (i), (ii), and (iii) the theorem is almost empty; such a category of fractions exists under negligible assumptions. (Added later: unfortunately there is no reason why the result should be a small category.) Our object, of course, is construct $F$ in such a way that we obtain a good hold on it. Parts (iv) and (v) essentially describe two ways of constructing $F$. We shall write  $\left[ X,Y \right] _{\ast}^E$ to mean the morphisms from $X$ to $Y$ in category $F$. Beside constructing  $F$, we must also give results calculating  $\left[ X,Y \right] _{\ast}^E$ in various cases which arise in the applications. When we construct the Adams spectral sequence, based on the homology theory $E_{\ast}$ we will try to prove that it converges to  $\left[ X,Y \right] _{\ast}^E$.\\
Before proving \ref{thm:p3ch14.1}, I will finish stating some results which help to show what $F$ is. \\
We propose to get a hold on $\left[ X,Y \right]^E$ by showing that if we keep $Y$ fixed and vary $X$ which is representable in  $C$. Then we give means for recognizing the representing object, and finally we construct the representing object in an elementary way in special cases.
\begin{proposition} \label{prop:p3ch14.2}
The following conditions on $Y$ are equivalent. 
 \begin{enumerate}
   \item [(i)] $f\colon \left[ X,Y \right] _{\ast} \to \left[ X,Y \right]^E_{\ast} $ is an isomorphism for all $X$. 
   \item [(ii)] if $E_{\ast}(X)=0$, then $\left[ X,Y \right] _{\ast}$ = 0. 
\end{enumerate} 
if these equivalent conditions hold, we say that $Y$ is E-complete. This term can be justified by inspecting the special case $E=HZ _{P}$, which will be considered later. 
\end{proposition}
    As an example, we give:
    \begin{corollary} \label{cor:p3ch14.3}
    If $Y$ is an E-module spectrum, then $Y$ is E-complete and 
    $$
    T\colon \left[ X,Y \right] _{\ast} \to \left[ X,Y \right]^E _{\ast} \text{ is an isomorphism.}
    $$ 
    \begin{proof} 
        (From 14.2). Condition (ii) of \ref{prop:p3ch14.2} holds by \plscite{13.1}.
    \end{proof}  
    \end{corollary}
   \begin{theorem} \label{thm:p3ch14.4}
     \begin{enumerate} 
       \item [(i)] For any spectrum $Y$ there is an E-equivalence  $e^{\prime}\colon Y \to Z'$ such that Z is E-complete. 
       \item [(ii)] Such an E-equivalence is universal. That is, given any other E-equivalence $e^{\prime}\colon Y \to Z^{\prime}$, there exists a unique $f\colon Z^{\prime} \to Z$ such that $fe^{\prime}=e$.
\[\begin{tikzcd}
	&& {Z'} \\
	Y \\
	&& Z
	\arrow["{e'}", from=2-1, to=1-3]
	\arrow["e"', from=2-1, to=3-3]
	\arrow["f"', dashed, from=1-3, to=3-3]
\end{tikzcd}\]
\item [(iii)] Therefore, Z is unique up to canonical equivalence.
\item [(iv)] For such a Z we have an isomorphism
  $$
  \left[ X, Z  \right]_{\ast} \to [X,Y]^E_{\ast}. 
  $$ 
  given by $f \mapsto \te{T}(e)^{-1}T(f).$
     \end{enumerate}
     \textbf{Notes.} (iii) follows immediately from (ii). Since Z is defined up to canonical equivalence by Y, we may write it as a function of Y; we choose the notation  $Z = Y^E$, so that
     $$
     \left[ X,Y^E\right]_{\ast} = \left[ X,Y \right] ^E_{\ast}.
     $$ 
We will call $Y^E$ the E-completion of $Y$. Again, the term can be justified by considering the special case  $E=HZ _{p}$. Note that $(Y^E)^E=Y^E$, so that the term ``completion'' is justified.\\
We say that $X$ is \textit{connective} if there exists $n_{0} \in \mathbb{Z}$ such that $ \pi_{r}(X)=0$ for $r<n_{0}$. 
   \end{theorem}
   
   \begin{proposition} \label{prop:p3ch14.5}
     Suppose that E is a commutative ring-spectrum and $ \pi_{r}(E)=0$ for $r<0$; suppose also that $Y$ is connective. Then  $\left[ X,Y \right] ^E_{\ast}$ depends only on the ring $ \pi_{0}(E)$.\\
     For example,  $\left[ X,Y \right] ^E_{\ast}$ is the same whether $E=MUQ_{p}$ or $E=buQ_{p}$. The idea is that under these hypothese, the difference between $\left[ X,Y \right] ^E_{\ast}$ and $\left[ X,Y \right] _{\ast}$ is essentially arithmetical. \\
For the next result, we assume that $E$ is a commutative ring-spectrum, that  $ \pi_{r}(E)=0$ for $r<0$, and  $Y$ is connective.\\
\end{proposition}
 \begin{theorem} \label{thm:p3ch14.6}
\begin{enumerate} 
  \item [(i)] Suppose $ \pi_{0}(E)$ is a subring $R$ of the rationals. Then  $$
    Y^E = YR.
  $$ 
\item [(ii)] Suppose $ \pi_{0}(E)=Z_{m}$ and  $\pi_{r}(Y)$ is finitely generated for all r. Then, 
  $$
    Y^E = YI_{m},
  $$ 
  where $I_{m}$ is the ring of m-adic integers, $\displaystyle{\varprojlim_r}$ $\mathbb{Z}_{m^r}$. 
\item [(iii)] Suppose $ \pi_{0}(E)=\mathbb{Z}_{m}$ and the identity morphism $1\colon Y \to Y$ satisfies $m^e\cdot 1=0$. Then 
  $$
    Y^E = Y.
  $$ 
\end{enumerate}
\end{theorem}
   
  
Examples. 
\begin{enumerate} 
  \item [(ia)] Suppose $\pi_{0}(E)=Z$, then $Y^E=Y$ and $T\colon \left[X,Y\right]^{}_{\ast} \to \left[X,Y\right]^{E}_{\ast}$ is an isomorphism. 
  \item [(ib)] Suppose $ \pi_{0}(E)$ is a subring R of the rationals and X is a finite spectrum. Then 
    $$
      \left[X,Y\right]^{E}_{\ast} = \left[X,YI_{m}\right]^{}_{\ast} = \left[X,Y\right]^{}_{\ast} \otimes R \text{  by \plscite{6.7}}
    $$ 
  \item [(iia)] Suppose $ \pi_{0}(E)=Z_{m}$, $ \pi_{r}(Y)$ is finitely generated for all r and X is a finite spectrum. Then
    $$
      \left[X,Y\right]^{E}_{\ast} = \left[X,YI_{m}\right]^{}_{\ast} = \left[X,Y\right]^{}_{\ast} \otimes I_{m} \text{  by \plscite{6.7}}
    $$ 
  \item [(iib)] Take m to be a prime p, and take X = Y = S. Then
    $$
    \left[S,S\right]^{E}_{r} = 
      \begin{cases} 
        0 & (r<0)\\
        1_{p} & (r=0)\\
        \text{the p-component of of $\left[S,S\right]^{}_{r}$ if $r>0$}.  
      \end{cases}
    $$ 
\end{enumerate}
It is very plausible that the classical Adams spectral sequence should converge to these groups.
\textit{Warnings.} 
\begin{enumerate} 
  \item [(i)] We have assumed that $\pi_{r}(E)=0$ for $r<0$. If we do not have this, the relationship between $\left[X,Y\right]_{\ast}$ and $\left[X,Y\right]^E _{\ast}$ may be much more distant. For example, take $E=K$; it can be shown that $\left[S,S\right]^K_{r} \neq 0$ for infinitely many negative values of r.

    \item [(ii)] Consider parts (ii) and (iii) of the theorem, in which $\pi_{0}(E)=\mathbb{Z}_{m}$. Results of the form given do require some assumption on Y beyond the fact it is connective. For example, take $Y = S(Q\setminus Z)$ It can be shown that 
      $$
        \left[S,Y\right]_{1} = 0 \text{  and so } \left[S,Y\right]_{1} \otimes I_{m} = 0, \text{  but } \left[S,Y\right]^E _{I} = I_{m}.
      $$ 
  If one takes m to be a prime p and checks the behavior of the classical Adams spectral sequence based on $E=HZ_{p}$, one sees that it converges to $ \left[S,Y\right]^E _{1}$, as indeed it must do by the theorem so be proved in the next section. So something which was previously a counterexample can now be used as evidence to support the theory.
\end{enumerate}
The proof of Theorem \ref{thm:p3ch14.1} requires two lemmas.
\begin{lemma} \label{lem:p3ch14.7}
\begin{enumerate} 
 \item [(i)] Suppose given a diagram

   \adjustbox{scale=0.8,center}{%
      \begin{tikzcd}
   	X &&& {X'} \\
   	\\
   	\\
   	Y
   	\arrow["f", from=1-1, to=1-4]
   	\arrow["e"', from=1-1, to=4-1]
     \end{tikzcd}
   } 
in which e is an E-equivalence. Then we can complete it to a commutative diagram 

\adjustbox{scale=0.8, center}{%
\begin{tikzcd}
	X &&&& {X'} \\
	\\
	\\
	Y &&&& {Y'}
	\arrow["e", from=1-1, to=4-1]
	\arrow["f"', from=1-1, to=1-5]
	\arrow["{e'}"', from=1-5, to=4-5]
	\arrow["g"', from=4-5, to=4-1]
\end{tikzcd} 
} 
in which $e^{\prime}$ is an E-equivalence. If f is also an E-equivalence, so is g.
\item [(ii)] Suppose given a diagram 

      \adjustbox{scale=0.8, center}{%
      \begin{tikzcd}
      	&&& {X'} \\
      	\\
      	\\
      	Y &&& {Y'}
      	\arrow["g", from=4-1, to=4-4]
      	\arrow["{e'}"', from=1-4, to=4-4]
      \end{tikzcd}
      } 
      in which $e^{\prime}$ is an E-equivalence. Then we can complete it to a commutative diagram 
~\\~\\
\adjustbox{scale=0.8, center}{%
\begin{tikzcd}
	X &&&& {X'} \\
	\\
	\\
	Y &&&& {Y'}
	\arrow["e", from=1-1, to=4-1]
	\arrow["f"', from=1-1, to=1-5]
	\arrow["{e'}"', from=1-5, to=4-5]
	\arrow["g"', from=4-5, to=4-1]
\end{tikzcd} 
} ~\\~\\
in which e is an E-equivalence. If g is also an E-equivalence, so is f.
  \end{enumerate}
\begin{proof} 
  \begin{enumerate} 
    \item [(i)] Let W be the fibre of $X \to X^{\prime}$, and let $Y^{\prime}$ be the cofibre of $W \to Y$. The morphism $e^{\prime}$ is an E-equivalence by the five lemma.
      \item [(ii)]  Part (ii) is similar. 
  \end{enumerate}   
\end{proof}
  \end{lemma}
\begin{lemma} \label{lem:p3ch14.8}
\begin{enumerate} 
\item [(i)] Suppose given 
  $$
  X^{\prime} \xrightarrow{e} X \overunderset{f}{g}{\rightrightarrows} Y
  $$ 
  Where $e^{\prime}$ is an E-equivalence and fe=ge. Then we can construct 
  $$
  X \overunderset{f}{g}{\rightrightarrows} Y \xrightarrow{e'} Y'
  $$ 
  with $e^{\prime}$ an $E$-equivalence and  $e^{\prime}f=e^{\prime}g$.
  \item [(ii)] Suppose given 
    $$
  X \overunderset{f}{g}{\rightrightarrows} Y \xrightarrow{e'} Y'
    $$ 
      Where e' is an E-equivalence and e'f=e'g. Then we can construct
  $$
  X^{\prime} \xrightarrow{e} X \overunderset{f}{g}{\rightrightarrows} Y
  $$ 
with e an E-equivalence and fe=ge.
\end{enumerate}
\begin{proof} 
  The proof is a manipulation with cofibering using Veridier's axiom (\plscite{6.8}) and is left as an exercise.\\
  Now, to contrusct F, let the object of F be the same as the objects of C. To define morphism in F, say $ \left[X,Y\right]^E $, one makes a preliminary construction. Fix Y, and consider the category in which the objects are E-equivalences. $Y \xrightarrow{e^{\prime}} Y^{\prime}$ and morphisms are diagrams of the following form.\\
  \adjustbox{scale=0.8, center}{%
  \begin{tikzcd}
  	&&& {Y'} \\
  	Y \\
  	&&& {Y''}
  	\arrow["{e'}", from=2-1, to=1-4]
  	\arrow["{e''}"', from=2-1, to=3-4]
  	\arrow[from=1-4, to=3-4]
  \end{tikzcd}
  } 
  Then \ref{lem:p3ch14.7} and \ref{lem:p3ch14.8} say that we get a directed category in the sense of Grothendieck. That is, given two objects A and B, there exists 
  \adjustbox{scale=0.8, center}{%
  \begin{tikzcd}
  	A \\
  	&&& {C;} \\
  	B
  	\arrow[from=1-1, to=2-4]
  	\arrow[from=3-1, to=2-4]
  \end{tikzcd}
  } 
  given two morphisms $ A \overunderset{f}{g}{\rightrightarrows} B  $, there exists $  A \overunderset{f}{g}{\rightrightarrows} B \xrightarrow{h} C$ where $hf = hg$.
\end{proof}
\end{lemma}

We define $\left[X,Y\right]^E_{\ast} = \displaystyle{\lim_{ \to }} \left[X,Y^{\prime}\right] $, where the direct limit takes place over this desired category. An element of $\displaystyle{\lim_{ \to } \left[X,Y^{\prime}\right]}$ is an equivalence class of diagrams  \\
\adjustbox{scale=0.8, center}{%
\begin{tikzcd}
        &&& {Y'} \\
        \\
        X &&& Y
        \arrow["{f'}", from=3-1, to=1-4]
        \arrow["{e'}"', from=3-4, to=1-4]
\end{tikzcd}
} ~\\~\\
in which $e^{\prime}$ is an $E$-equivalence. Two such diagrams are equivalent if and only if there exists a diagram of the following form.

\[\begin{tikzcd}
	&&&&& {Y_1} \\
	X &&&& Y && {Y'} \\
	&&&&& {Y_2}
	\arrow["{f_1}", from=2-1, to=1-6]
	\arrow["{f_2}"', from=2-1, to=3-6]
	\arrow["{e_1}"', from=2-5, to=1-6]
	\arrow["{e'_1}"', from=1-6, to=2-7]
	\arrow["{e'_2}"{description}, from=3-6, to=2-7]
	\arrow["{e_2}"{description}, from=2-5, to=3-6]
\end{tikzcd}\]
This is essentially the construction presented in (iv). To check that this is an equivalence relation one uses \ref{lem:p3ch14.7} {i}.

To define composition in the category, suppose given the two diagrams shown below with undotted arrows.

\adjustbox{scale=0.8, center}{%
\begin{tikzcd}
	&&&&&& {Z''} \\
	\\
	&&& {Y'} && {Y'} \\
	\\
	X && Y && Z
	\arrow["{f_1}", from=5-1, to=3-4]
	\arrow["{e_1}"', from=5-3, to=3-4]
	\arrow["{f_2}", from=5-3, to=3-6]
	\arrow["{e_2}"', from=5-5, to=3-6]
	\arrow[dashed, from=3-4, to=1-7]
	\arrow[dashed, from=3-6, to=1-7]
\end{tikzcd}
} 
~\\~\\Add the dotted arrows by \ref{lem:p3ch14.7} {i}. We get a diagram representing a morphism from X to Z in the new category. We check that the equivalence class of this diagram depends only on the equivalence classes of the factors, not on the choice of parallelogram (use \ref{lem:p3ch14.7} (i), \ref{lem:p3ch14.8} (i)).

We check the associativity law and the existence of identity morphisms. We now have a category F. We define $T:\colon C \to F$ as follows: if $f\colon X \to Y$, let T(f) be the class of the following diagram.
~\\
\adjustbox{scale=0.8, center}{%
\begin{tikzcd}
	&&& Y \\
	\\
	X &&& Y
	\arrow["f", from=3-1, to=1-4]
	\arrow["1"', from=3-4, to=1-4]
\end{tikzcd}
} 
One checks that this is a functor, It is now almost trivial to verify properties (i)-(iv)) of the theorem.

On the other hand, precisely the dual construction works using \ref{lem:p3ch14.7} (ii) and \ref{lem:p3ch14.8} (ii) to show that one can construct F so as to have properties (i)-(iii) and (v). But of course F is characterized by (i)-(iii), so it must have both properties (iv) and (v). 

Now we turn to Proposition \ref{prop:p3ch14.2}. First, suppose $E_{\ast}(X)=0$. Then it is clear that the morphism $pt. \to X$ is cofinal among E-equivalences. $e^{\prime}\colon X^{\prime} \to X$. So we have $ \left[X,Y\right]_{\ast} = 0$. If we assume that $T\colon \left[X,Y\right]_{\ast} \to \left[X,Y\right]^E_{\ast}=0$ is an isomorphism, then clearly we deduce that $ \left[X,Y\right]_{\ast}=0$. So condition (i) of \ref{prop:p3ch14.2} implies condition (ii). The proof that(ii) implies (i) will be given together with the proof of part of Theorem \ref{thm:p3ch14.4} to be considered below. This requires three lemmas, numbered \ref{lem:p3ch14.9}, \ref{lem:p3ch14.10}, and \ref{lem:p3ch14.11}. 
\begin{lemma} \label{lem:p3ch14.9}
Let $A \to B \to C$ be a cofibering. Then
$$
  \left[A,Y\right]^E_{\ast} \longleftarrow \left[B,Y\right]^E_{\ast} \longleftarrow \left[C,Y\right]^E_{\ast}
$$ 
and
$$
  \left[X,A\right]^E_{\ast} \to \left[X,B\right]^E_{\ast} \to  \left[X,C\right]^E_{\ast}
$$ 
are exact.
\begin{proof} 
   For any $Y^{\prime}$, the sequence 
   $$
     \left[A,Y^{\prime}\right] \longleftarrow \left[B,Y^{\prime}\right]_{\ast} \longleftarrow \left[C,Y^{\prime}\right]_{\ast}
   $$ 
   is exact. The given sequence is obtained from such sequences by passing to a direct limit. But direct limits over a directed category preserve exactness. The same form of argument holds for the second sequence, using the fact that we can also define $ \left[X,Y\right]^E_{\ast}$ by taking a direct limit of $ \left[X^{\prime},Y\right]_{\ast}$ as we vary $X^{\prime}$.
\end{proof}
\end{lemma}
\begin{lemma} \label{lem:p3ch14.10}
The canonical map 
$$
  \left[\bigvee_{\alpha}X_{\alpha},Y\right]^E_{\ast} \to \prod_{a} \left[X_{\alpha},Y\right]^E_{\ast}
$$ 
is an isomorphism.
\begin{proof}
  \begin{enumerate} 
    \item [(i)] Suppose given an element in $\prod_{a}\left[X_{a},Y\right]^E;$ each of its components is represented by a diagram\\~\\
      \adjustbox{scale=0.8, center}{%
      \begin{tikzcd}
      	& {X_{\alpha}} &&& Y \\
      	\\
      	{X'_{\alpha}}
      	\arrow["{e_{\alpha}}", from=3-1, to=1-2]
      	\arrow["{f_{\alpha}}"', from=3-1, to=1-5]
      \end{tikzcd}
      } 
      Then we can form the diagram 
      ~\\~\\
      \adjustbox{scale=0.8, center}{%
      \begin{tikzcd}
      	&& {\bigvee_{\alpha}X_{\alpha}} &&& Y \\
      	\\
      	{\bigvee_{\alpha}X'_{\alpha}}
      	\arrow["{\bigvee_{\alpha}e_{\alpha}}", from=3-1, to=1-3]
      	\arrow["{\{f_\alpha\} }"', from=3-1, to=1-6]
      \end{tikzcd}
      }  
      ~\\~\\
      This gives an element of $ \left[\bigvee_{\alpha} X_{\alpha} , Y \right]^E_{\ast}$ which maps the required way.
      \item [(ii)] Suppose given an element of $\left[\bigvee_{\alpha} X_{\alpha}, Y \right]^E_{\ast}$, say represented by 
        ~\\~\\
        \adjustbox{scale=0.8, center}{%
        \begin{tikzcd}
        	&& {\bigvee_{\alpha}X_\alpha} &&& Y \\
        	\\
        	{W'}
        	\arrow["e", from=3-1, to=1-3]
        	\arrow["f"', from=3-1, to=1-6]
        \end{tikzcd}
        }  
        ~\\~\\
       Suppose it restricts to zero in each  $ \left[X_{\alpha},Y\right]^E_{\ast}$. This says that for each $\alpha$ we have a commutative diagram of the following form;
       ~\\~\\
       \adjustbox{scale=0.8, center}{%
       \begin{tikzcd}
       	{X_\alpha} &&& {\bigvee_{\alpha}X_\alpha} &&& Y \\
       	\\
       	{X_\alpha} &&& {W'} \\
       	\\
       	{X'_\alpha}
       	\arrow["1", from=3-1, to=1-1]
       	\arrow["{e_\alpha}", from=5-1, to=3-1]
       	\arrow["{i_\alpha}", from=3-1, to=1-4]
       	\arrow["{j_\alpha}"', from=5-1, to=3-4]
       	\arrow["f"', from=3-4, to=1-7]
       	\arrow["e"', from=3-4, to=1-4]
       \end{tikzcd}
       }  
       ~\\~\\
       and moreover, $fj_{\alpha}=0$. Then consider the following diagram.
       ~\\~\\
       \adjustbox{scale=0.8, center}{%
       \begin{tikzcd}
       	&&& {\bigvee_{\alpha}X_\alpha} &&& Y \\
       	\\
       	&&& {W'} \\
       	\\
       	{\bigvee_{\alpha}X'_\alpha}
       	\arrow["{\bigvee_{\alpha}e_\alpha}", from=5-1, to=1-4]
       	\arrow["e"', from=3-4, to=1-4]
       	\arrow["{\{j_\alpha\}}"', from=5-1, to=3-4]
       	\arrow["f"', from=3-4, to=1-7]
       \end{tikzcd}
       }  
       ~\\~\\
       This shows that the diagram
       ~\\~\\
       \adjustbox{scale=0.8, center}{%
       \begin{tikzcd}
       	&& {\bigvee_{\alpha}X_\alpha} &&& Y \\
       	\\
       	{W'}
       	\arrow["e"', from=3-1, to=1-3]
       	\arrow["f"', from=3-1, to=1-6]
       \end{tikzcd}
       }  
       ~\\~\\
       gives the zero element of $ \left[\bigvee_{\alpha} X_{\alpha},Y\right]^E_{\ast}$. 
  \end{enumerate}
\end{proof}
\end{lemma}
Now we start the proof of \ref{thm:p3ch14.4}. Consider $ \left[X,Y\right]^E_{\ast}$. Hold Y fixed and vary X. By \ref{lem:p3ch14.9} and \ref{lem:p3ch14.10}, we have the data for E. H. Brown's Theorem, and we deduce that  $ \left[X,Y\right]^E_{\ast}$ is a representable functor of X. That is, there is a spectrum Z and a natural transformation
$$
U\colon  \left[X,Y\right]_{\ast} \xrightarrow{\cong}  \left[X,Y\right]^E_{\ast}
$$ 
Here Z satisfies condition (ii) of \ref{prop:p3ch14.2}. For suppose $E_{\ast}(X)=0$; then $ \left[X,Y\right]^E_{\ast}=0$, as we have remarked; so $ \left[X,Y\right]_{\ast}=0$, since U is an isomorphism.

Now consider $1 \in \left[ Z,Z \right] $ and $U(1) \in \left[Z,Y\right]^E  $. the latter is represented by this diagram
~\\~\\
\adjustbox{scale=0.8, center}{%
\begin{tikzcd}
	&&& {Y'} \\
	&& {} \\
	\\
	Z && Y
	\arrow["u", from=4-1, to=1-4]
	\arrow["{e'}"', from=4-3, to=1-4]
\end{tikzcd}
}  
~\\~\\
Extend this to a cofibre sequence 
~\\~\\
\adjustbox{scale=0.8, center}{%
\begin{tikzcd}
	&&&&&& {Y'} \\
	\\
	&& Z &&& Y \\
	\\
	X
	\arrow["f", from=5-1, to=3-3]
	\arrow["u", from=3-3, to=1-7]
	\arrow["{e'}"', from=3-6, to=1-7]
\end{tikzcd}
}  
~\\~\\
Then by naturality $U(f)=f^\ast U(1)=0$. Since $U$ is a monomorphism, $f=0$. Therefore the morphism $Z\xrightarrow{u} Y^{\prime}  $ is equivalent to the injection $Z  \to Z_{\vee}\te{Susp}(X);$ we can replace the representative for U(1) by the following diagram.
~\\~\\
\adjustbox{scale=0.8, center}{%
\begin{tikzcd}
	&&&& {Z_{\vee}\mathrm{Susp}(X)} \\
	\\
	\\
	Z &&& Y
	\arrow["i", from=4-1, to=1-5]
	\arrow["{e''}", from=4-4, to=1-5]
\end{tikzcd}
}  
~\\~\\

Now consider $1 \in \left[Y,Y\right]^E_{\ast}$; there exists $\epsilon\colon Y  \to Z $ such that $\te{\epsilon} = 1 \in \left[Y,Y\right]^E $. That is, we have the following commutative diagram.
~\\~\\
\adjustbox{scale=0.8, center}{%
\begin{tikzcd}
	&&& {Z_{\vee}\mathrm{Susp}(X)} \\
	& Z \\
	\\
	Y && Y && {Y''} \\
	\\
	&&& Y
	\arrow["1", from=4-1, to=6-4]
	\arrow["1"', from=4-3, to=6-4]
	\arrow["{e_2}"', from=6-4, to=4-5]
	\arrow["\epsilon"', from=4-1, to=2-2]
	\arrow["i"', from=2-2, to=1-4]
	\arrow["{e''}", from=4-3, to=1-4]
	\arrow["{e_1}", from=4-5, to=1-4]
\end{tikzcd}
}  
~\\~\\
We conclude that $i_{\ast}: E_{\ast}(Z) \to E_{\ast}(Z_{\vee}\te{Susp}(X))$ is an ebimorphism.
Therefore $E_{\ast}(Z_{\vee}\te{Susp}(X))=0$. Hence, $i_{\ast}: E_{\ast}(Z) \to E_{\ast}(Z_{\vee}\te{Susp}(X))$ and $ \epsilon_{\ast}: E_{\ast}(Y) \to E_{\ast}(Z)$ are isomorphisms.

Since we now know that $\epsilon\colon Y  \to Z $ is an E-equivalence, we allow ourselves to change its name to $e\colon  Y \to  Z $. We have proved that any spectrum $Y$ admits an E-equivalence $e\colon  Y \to  Z $, where $E_{\ast}(X)=0$ implies $ \left[X,Y\right]_{\ast}=0$. 

We will now forget everything about Z except these two properties.
\begin{lemma} \label{lem:p3ch14.11}
Suppose $e\colon  Y \to  Z $ is an E-equivalence, and  $E_{\ast}(X)=0$ implies $ \left[X,Y\right]_{\ast}=0$. Then \ref{thm:p3ch14.4} (ii) and (iv) hold. \\
This will complete the proof of Proposition \ref{prop:p3ch14.2}; for we take $e\colon  Y \to  Z $ to be  $1\colon  Y \to  Y $, and deduce that 
$$
  T\colon  \left[X,Y\right]_{\ast} \to \left[X,Y\right]^E_{\ast}  
$$ 
is an isomorphism. Moreover, it will obviously complete the proof of \ref{thm:p3ch14.4}. 
\begin{proof} 
    We have to show that $e\colon  Y \to  Z $ is universal. Suppose given an E-equivalence $e^{\prime}\colon  Y \to  Z^{\prime} $. Then up to equivalence we have $Z^{\prime}= Y \displaystyle{\bigcup_{g}} CA $ for some $g\colon  A \to  Y $; and here $E_{\ast}(A)=0$, by the exact sequence of the cofibering $A \to Y \xrightarrow{e^{\prime}} Z^{\prime}$.
    ~\\~\\
    \adjustbox{scale=0.8, center}{%
\begin{tikzcd}
	&&&&&& A \\
	\\
	&&&& {Z'} \\
	\\
	&& Y &&&& Z && {\text{(j has degree -1).}} \\
	\\
	A
	\arrow["g", from=7-1, to=5-3]
	\arrow["{e'}", from=5-3, to=3-5]
	\arrow["j", from=3-5, to=1-7]
	\arrow["e", from=5-3, to=5-7]
	\arrow[dashed, from=3-5, to=5-7]
\end{tikzcd}
    }  
    ~\\~\\
 Then eg = 0 by the assumed property of Z, so e extends over $Y \displaystyle{\bigcup_{g}}  CA$ and there is a map $f\colon  Z^{\prime} \to  Z $ with $fe^{\prime}=e$. Also f is unique, because two choices differ by an element of $j^\ast\left[A,Z\right]_{\ast}$, and $ \left[A,Z\right]_{\ast}=0$ by the assumed property of Z.   

This shows that $e\colon  Y \to  Z $ is universal. Then clearly the single object $Y\xrightarrow{e} Z$ is cofinal in the directed category used to construct $ \left[X,Y\right]^E_{\ast}$ so we have an isomorphism
$$
  \left[X,Y\right]_\ast \to \left[X,Y\right]^E_{\ast} 
$$ 
given by assigning to a morphism $f\colon  X \to  Z $ the class of the diagram
~\\~\\
\adjustbox{scale=0.8, center}{%
\begin{tikzcd}
	&&&& Z \\
	\\
	\\
	X &&& Y
	\arrow["f", from=4-1, to=1-5]
	\arrow["e"', from=4-4, to=1-5]
\end{tikzcd}
}  
~\\~\\
i.e., the element $T(e)^{-1}T(f) \in \left[X,Y\right]^E_{\ast}$. This completes the proof of \ref{prop:p3ch14.2}, \ref{cor:p3ch14.3}, and \ref{thm:p3ch14.4}.
\end{proof}
\end{lemma}
Now we start working toward the proof of \ref{prop:p3ch14.5}.

\begin{lemma} \label{lem:p3ch14.12}
Suppose $ \pi_{r}(E)=0$ for $r<0$. Suppose a morphism $f\colon  X \to  Y $ induces an isomorphism $E_{\ast}(X) \to E_{\ast}(Y)$. Then it induces an isomorphism $H_{\ast}(X, \pi_{0}(E)) \to H_{\ast}(Y;\pi_{0}(E))$. 
\begin{proof} 
    First a remark. Let E be any spectrum, not necessarily a ring-spectrum, and not necessarily connective; then I claim
    $$
      H \wedge E \simeq \bigvee_{i} S^i \wedge HG_i, 
    $$ 
    Where $G_{i} = H_{i}(E)$. In fact, for each i we can construct a Moore spectrum $S^iG_{i};$ then we can construct a morphism
    $$
      S^iG_{i} \xrightarrow{a_{i}} H \wedge E 
    $$ 
    inducing the identity map
    $$
      G_{i} = \pi_{i}(S^iG_{i}) \to \pi_{i}(H \wedge E)= G_{i}.
    $$ 
    Now we can form 
    $$
      H \wedge (S^iG_i) \xrightarrow{1 \wedge a_{i}} H \wedge H \wedge E \xrightarrow{\mu \wedge 1} H \wedge E.  
    $$ 
    Finally we form 
    $$
      \bigvee_{i} H \wedge (S^iG_{i}) \xrightarrow{\{(\mu \wedge 1) (1 \wedge a_{i})\} } H \wedge E.
    $$ 
    This induces an isomorphism of homotopy groups, so it is an equivalence by the theorem of J. H. C. Whitehead.

    Now we return to the lemma. From the cofibering $X\xrightarrow{f} Y \to Z$. Then we have $E_{\ast}(Z)=0$ and it is sufficient to deduce that $H_{\ast}(Z;\pi_{0}(E)=0)$. Since $ \pi_{\ast}(E \wedge Z)=0, E \wedge Z$ is contractible. Therefore $H \wedge E \wedge Z$ is contractible. Now $ \pi_{r}(E)=0$ for $r<0$, so by the Hurewicz theorem $ G_0 = H_0(E) = \pi_{0}(E)$. We have just shown that $HG_0$ is a direct summand in $H \wedge E$, so $(HG_0) \wedge Z$ is contractible; that is $H_{\ast}(Z; \pi_{0}(E))=0$. This proves the lemma.
\end{proof}

\end{lemma}

\begin{lemma} \label{lem:p3ch14.13}
Suppose E is a commutative ring-spectrum and $ \pi_{r}(E)=0$ for $r<0$. Suppose X and Y are connective and $f\colon  X \to  Y $ induces an isomorphism $H_{\ast}(X;\pi_{0}(E)) \to H_{\ast}(Y, \pi_{0}(E))$. Then it induces an isomorphism $E_{\ast}(X) \to E_{\ast}(Y)$.

\begin{proof} 
  As before, we form the cofibering $X \xrightarrow{f} Y \to Z$. Then Z is connective; we have $H_{\ast}(Z;\pi_{0}(E))$, and it is sufficient to prove $E_{\ast}(Z)=0$.

  Since $ \pi_{0}(E)$ is a commutative ring and $ \pi_{r}(E)$ is a module over $ \pi_{0}(E)$, we have the universal coefficient theorem in the form of the spectral sequence
  $$
  \te{Tor}_{P_{\ast}}^{\pi_{0}(E)}  H_{P}(Z;\pi_{q}(E)), \pi_{r}(E)) \underbrace{\implies}_{P} H_{\ast}(Z;\pi_{r}(E)). 
  $$ 
  This is a quarter-plan spectral sequence convergent in the naive sense. We see that $H_{\ast}(Z;\pi_{0}(E))=0$. We now consider the Atiyah-Hirzebruch spectral sequence
  $$
    H_{p}(Z;\pi_{q}(E)) \underbrace{\implies}_{p} E_{p+q} (Z). 
  $$ 
  This is a quarter-plane spectral sequence convergent in the naive sense. We conclude that $E_{\ast}(Z)=0$.
\end{proof}
\emph{Warning.} This condition that X and Y are connective cannot be omitted (take E = bu, X=pt., $Y=BUZ_P$ or vice versa).
\end{lemma}

\begin{proof}[Proof of 14.5.] 
  recall that we wish to show that if E is a commutative ring spectrum and $\pi_{r}(E)=0$ for $r<0$, then for any connective spectrum Y, $\left[X,Y\right]^E_{\ast}$ depends only on  $\pi_{0}(E)$. More precisely, we show that $\left[X,Y\right]^E_{\ast}=\left[X,Y\right]^{E^{\prime}}_{\ast}$, where $E= H \pi_{0}(E)$.
  \begin{enumerate} 
    \item [(i)] By \ref{lem:p3ch14.12}, we have that any morphism $f\colon  Y \to  Y^{\prime} $ which induces an isomorphism in E-homology also induces an isomorphism in $E^{\prime}$-homology.
    \item [(ii)] Consider the directed category used in the construction of $\left[X,Y\right]^{E^{\prime}}_{\ast}$. I claim that morphism $f\colon  Y \to  Y^{\prime} $ which induce an isomorphism in E-homology are cofinal in those which induce an isomorphism in $E^{\prime}$-homology. Once this is proved, \ref{prop:p3ch14.5} follows. We need a lemma.
  \end{enumerate}
\end{proof}

\begin{lemma} \label{lem:p3ch14.14}
Let Y be a connective spectrum. X any spectrum. Then any morphism $f\colon  X \to  Y $ factors as 
~\\~\\
\adjustbox{scale=0.8, center}{%
\begin{tikzcd}
	X && Y \\
	\\
	& {X'}
	\arrow[from=1-1, to=1-3]
	\arrow[from=1-1, to=3-2]
	\arrow[from=3-2, to=1-3]
\end{tikzcd}
}  
~\\~\\
Where $X^{\prime}$ is connective and $H_{r}(X^{\prime}) \begin{cases}\simeq H_{r}(X) & (r \ge N)\\ =0 & (r < N)\end{cases}$ for some $N \in Z$ depending only on Y. 
\begin{proof} 
  Let N be such that $\pi_{r}(Y)=0$ for $r < N + 1$. Then we can factor f through  $X\setminus X^{N-1}$; this spectrum is connective. However, it need not have the desired properties in homology. We have
  \begin{align*}
    H_{r}(X \setminus X^{N-1}) &\cong H_{r}(X) &&(r > N) \\[0.5em]
    H_{r}(X \setminus X^{N-1}) &= 0   &&(r < N)
  \end{align*}
  and in dimension N we have an exact sequence 
  $$
    0 \to H_{N}(X) \to H_{N} (X \setminus X^{N-1}) \to F \to 0,
  $$ 
  where F is free since it is a subgroup of $H_{N-1}(X^{N-1})$. By the Hurewicz theorem, we have 
  $$
    \pi_{N}(X \setminus X^{N-1})\cong H_{N} (X \setminus X^{N-1}). 
  $$ 
  Choose a set of elements
  $$
    \theta_{\alpha} \in \pi_{N}(X \setminus X^{N-1})
  $$ 
  which project to a base of F, and form
  $$
    X^{\prime} = X \setminus X^{N-1} \bigcup_{\theta_{\alpha}} CS^N. 
  $$ 
  $X^{\prime}$ is connective, and $X \setminus X^{N-1} \to Y$ factors through $x^{\prime}$. We have
  $$
  H_{r}(X^{\prime})
    \begin{cases} 
      \cong H_{r}(X) & (r \ge N)\\
      =0 & (r < N).
    \end{cases}
  $$ 
  Returning to (ii) above, suppose $f\colon  Y \to  Y^{\prime} $ induces an isomorphism in $E^{\prime}$-homology. Form a cofibre sequence 
  $$
    A \to Y \xrightarrow{f} Y^{\prime} \to \ldots
  $$ 
  Here  $H_{r}(A;\pi_{0}(E))=0$, and so by the ordinary universal coefficient theorem.
  $$
  H_{r}(A)\otimes_{Z} \pi_{0}(E)=0, \qquad \te{Tor}^Z_{1} (H_{r}(A), \pi_{0}(E))=0.
  $$ 
  By \ref{lem:p3ch14.14}, we can factor $A\to Y$ in the form
  ~\\~\\
  \adjustbox{scale=0.8, center}{%
  \begin{tikzcd}
  	A && {Y,} \\
  	\\
  	& B
  	\arrow[from=1-1, to=3-2]
  	\arrow[from=1-1, to=1-3]
  	\arrow[from=3-2, to=1-3]
  \end{tikzcd}
  }  
  ~\\~\\
 Where B is connective and 
 \begin{align*}
   &H_{r}(A) \xrightarrow{\cong} H_{r}(B)  &&\text{for $r\ge N$}\\[0.5em]
   &H_{r}(B) =  0    &&\text{for $r < N$}.
 \end{align*} 
 Then 
 $$
 H_{r}(B) \otimes_{Z} \pi_{0}(E)=0, \te{Tor}^Z_{1} (H_{r}(A), \pi_{0}(E))=0 
 $$ 
 and so 
 $$
   H_{r}(B; \pi_{0}(E))=0 
 $$ 
 for all r. Now we can form the following diagram of cofiberings.
 ~\\~\\
 \adjustbox{scale=0.8, center}{%
 \begin{tikzcd}
 	A && Y && {Y'} && \ldots \\
 	\\
 	B && Y && {Y''} && \ldots
 	\arrow[from=1-1, to=3-1]
 	\arrow[from=1-1, to=1-3]
 	\arrow[from=3-1, to=3-3]
 	\arrow["1"', from=1-3, to=3-3]
 	\arrow["f"', from=1-3, to=1-5]
 	\arrow[from=3-3, to=3-5]
 	\arrow[from=1-5, to=3-5]
 	\arrow[from=1-5, to=1-7]
 	\arrow[from=3-5, to=3-7]
 \end{tikzcd}
 }  
 ~\\~\\
 Here $Y^{\prime\prime}$ is connective, and $Y \to Y^{\prime\prime}$ is an $E^{\prime}$-equivalence, so it is an E-equivalence by \ref{lem:p3ch14.13} proof of (iii) above, and so completes the proof of  \ref{prop:p3ch14.5}
\end{proof}
\end{lemma}

Now we turn to Theorem \ref{thm:p3ch14.6}. We have to take $YR$, or  $YI_{m}$, or Y, according to the case, and show it satisfies the conditions in \ref{thm:p3ch14.4}. We have already shown that it will be sufficient to check \ref{thm:p3ch14.4} (i), that is to say that these spectra are E-equivalent to Y, under the hypotheses given for each case, and E-complete. 

Consider the first condition. In case (i), suppose $\pi_{0}(E)$ is a subring $R$ of the rationals Z. Consider the product 
 $$
  SR \wedge S(R\setminus Z).
$$ 
By the Kunneth theorem we have 
$$
  H_{\ast}(SR \wedge S(R \setminus Z)) =0; 
$$ 
for $R \otimes_{Z} (R\setminus Z)=0, \te{  Tor}^Z_{1}(R, R \setminus Z)=0$, The spectrum is connective, so $SR \wedge S(R \setminus Z)$ is contractible by the theorem of J. H. C. Whitehead. 

Now we have a cofibering 
$$
  Y \to YR \to Y \wedge S ( R \setminus Z).
$$ 
Here we have 
$$
  HR_{\ast}(Y \wedge S (R \setminus Z)) = \pi_{\ast}(H \wedge SR \wedge Y \wedge S(R \setminus Z))=0, 
$$ 
for $H \wedge SR \wedge Y \wedge S(R \setminus Z$ is contractible. So
$$
(HR)_{\ast}(Y) \to (HR)_{\ast}(YR)
$$ 
is an isomorphism. 

We proceed similiarly for case (ii), starting from the fact that $SZ_{m} \wedge S ( I_{m} \setminus Z)$ is contractible. 

In case (iii) it is trivial that $Y \xrightarrow{1} Y $ is an E-equivalence.

Now we have to check the other condition of \ref{thm:p3ch14.4}, namely that $E_{\ast}(X)=0$ implies $\left[X,YR\right]_{\ast}=0,$ or $\left[X,YI_{m}\right]_{\ast}=0$, or $\left[X,Y\right]_{\ast}=0$ according to the case.

First suppose that we are in case (i), so that $\pi_{0}(E)=R$. Suppose that $f\colon  X \to  YR $ is a map, and suppose I have already deformed it until all the stable n-cells map to the base-point. (The induction starts, because YR is connective.) I wish to keep it is fixed on the (n-1)-cells and deform it until the n-cells and (n+1)-cells map to the base point.

There is an obstruction, and it lies in $H^{n+1}(X;\pi_{n+1}(YR))$. But R is a principal ideal ring, and $\pi_{n+1}(YR)$ is a module over R, so the ordinary universal coefficient theorem applies; we know $H_{\ast}(X;R)=0$, so we can deduce 
$$
H^{n+1}(X;\pi_{n+1}(YR))=0
$$ 
So I can deform f as required. I continue by induction and conclude that $f=0.$ This shows that  $\left[X,YR\right]_{\ast}=0$.

Evidently the obstruction-theory argument will work just as well in case (ii), provided we prove that 
$$
H^{n+1}(X;\pi_{n+1}(YI_{m}))=0
.$$
Here we have $\pi_{n+1}(YI_{m})=\pi_{n+1}(Y)\otimes I_{m}$ by \plscite{6.7}, and $\pi_{n+1}(Y)$ is a finitely-generated group. And in this case we start by knowing that 
$$
  H^\ast(X;Z_{m})=0.
$$ 
The exact sequence $0 \to Z \xrightarrow{m} Z \to Z_{m} \to 0 $ induces a long exact sequence in homology; it follows that $H_{\ast}(X) \xrightarrow{m} H_{\ast}(X) $ is an isomorphism, hence $H_{\ast}(X) \xrightarrow{m^t}  H_{\ast}(X)$ is an isomorphism. Now consider 
$$
\te{Hom}_{Z} (H_{r}(X), Z_{m^t}), \quad \te{Ext}^1_{Z}(H_{r}(X),Z_{m^t}).
$$ 
On the one hand multiplication by $m^t$ is an isomorphism; on the other hand it is zero. Hence the group must be zero. So by the ordinary universal coefficient theorem, 
 $$
  H^r(X;Z_{m^t}) = 0.
$$ 
Now we have an exact sequence 
$$
  0 \to \varprojlim^1 (H^\ast(X;Z_{m^t})) \to H^\ast(X;I_{m}) \to \varprojlim^0(H^\ast(X;Z_{m^t})) \to 0
$$ 
Hence we have $H^\ast(X;I_{m})=0$. Finally, let G be any finitely-generated abelian group. We have a resolution
$$
  0 \to F_1 \to F_0 \to G \to 0
$$ 
with $F_0$ and $F_1$ finitely-generated free. Therefore we have an exact sequence 
$$
  0 \to \prod_{1}^{r} I_{m} \to \prod_{1}^{s} I_{m} \to I_{m} \otimes G \to 0.  
$$ 
This yields an exact cohomology sequence, from which we conclude that 
$$
  H^\ast(X;I_{m} \otimes G)=0.
$$ 
We conclude that 
$$
H^{n+1}(X;\pi_{n+1}(YI_{m}))=0.
$$ 
the obstruction-theory argument works, and 
$$
  \left[X,YI_{m}\right]_{\ast}=0.
$$ 
Finally we consider case (iii). Let $f\colon  X \to  Y $ be a morphism. By Lemma \ref{lem:p3ch14.14}, we can factor f as 
~\\~\\
\adjustbox{scale=0.8, center}{%
\begin{tikzcd}
	X && Y \\
	\\
	& {X'}
	\arrow["f"{description}, from=1-1, to=1-3]
	\arrow[from=1-1, to=3-2]
	\arrow[from=1-3, to=3-2]
\end{tikzcd}
}  
~\\~\\
where $X^{\prime}$ is connective; $H_{r}(X^{\prime}) \cong H_{r}(X), r \ge N, $ and $H_{r}(X^{\prime}) =0$ for $r < N$, for some  $N \in Z$.

As above, 
$$
  m\colon  H_{\ast}(X)  \to  H_{\ast}(X)  
$$ 
is an isomorphism; clearly the same is true for $X^{\prime}$. Since $X^{\prime}$ is connective, the theorem of J. H. C. Whitehead shows that $m\colon  X^{\prime} \to  X^{\prime} $ is an equivalence; so it has an inverse $m^{-1}$. Consider the following diagram 
~\\~\\
\adjustbox{scale=0.8, center}{%
\begin{tikzcd}
	{X'} && {X'} && Y \\
	\\
	&& {X'} && Y
	\arrow["1", from=1-1, to=1-3]
	\arrow["{(m^{-1})^e}"', from=1-1, to=3-3]
	\arrow["{m^e}"', from=3-3, to=1-3]
	\arrow["{f'}"', from=1-3, to=1-5]
	\arrow["{m^e}", from=3-5, to=1-5]
	\arrow["{f'}", from=3-3, to=3-5]
\end{tikzcd}
}  
~\\~\\
Since $m^{e}\cdot 1_{Y}\colon Y \to Y$ is the zero morphism, we conclude $f^{\prime}=0.$ Thus $\left[X^{\prime},Y\right]_{\ast}=0$. This completes the proof of \ref{thm:p3ch14.6}.

Now we have some short lemmas, which will be needed in the next section
\begin{lemma} \label{lem:p3ch14.15}
Suppose
~\\~\\
\adjustbox{scale=0.8, center}{%
\begin{tikzcd}
	A && B \\
	\\
	& C
	\arrow[from=1-1, to=1-3]
	\arrow[from=1-3, to=3-2]
	\arrow[from=3-2, to=1-1]
\end{tikzcd}
}  
~\\~\\
is a cofibre triangle and two of $A,B,C$ are E-complete.; then so is the third.

 \begin{proof} 
    Suppose $E_{\ast}(X)\simeq 0.$ We have an exact sequence
    $$
      \left[X,A\right]_{\ast} \to \left[X,B\right]_{\ast} \to \left[X,C\right]_{\ast} \to \left[X,A\right]_{\ast} \to \ldots
    $$ 
    Two out of ever three groups are zero, so the third must be zero also.
\end{proof}
\end{lemma}
\begin{lemma} \label{lem:p3ch14.16}
If $f\colon  X \to  X^{\prime} $ and $g\colon  Y \to  Y^{\prime} $ are E-equivalences, so is 
$$
  f \wedge g \colon X \wedge Y \to X^{\prime} \wedge Y^{\prime} .
$$ 
This lemma says that smash products pass to the category of fractions.
\begin{proof} 
    We are given that $E \wedge X \xrightarrow{1 \wedge f} E \wedge X^{\prime} $ and $E \wedge Y \xrightarrow{1 \wedge g} E \wedge Y^{\prime}$ are equivalences. Then
    $$
      E \wedge X \wedge Y^{\prime} \xrightarrow{1\wedge f \wedge 1} E \wedge X^{\prime} \wedge Y^{\prime} 
    $$ 
    and 
    $$
      E \wedge X \wedge Y \xrightarrow{1\wedge 1 \wedge g} E \wedge X \wedge Y^{\prime} 
    $$ 
    are equivalences; hence so is their composite; that is,
    $$
    X \wedge Y \xrightarrow{f \wedge g} X^{\prime} \wedge Y^{\prime}
    $$ 
    is an E-equivalence.

    Now we introduce some arithmetical considerations. Let E be a commutative ring-spectrum such that $\pi_{r}(E)=0$ for $r < 0$, and let  $\theta\colon  Z \to  \pi_{0}(E) $ be the unique homomorphism of rings. Let $S \subset Z$ be the set of n such that $\theta(n)$ is invertible in $\pi_{0}(E)$. Then S is multiplicatively closed. Let $R \subset Q$ be the localization of Z at S, i.e., the set of fractions $n\setminus m$ with $m \in  S$. Then there exists a unique extension of $\theta$ to
    $$
      \theta\colon  R \to  \pi_{0}(E) .
    $$ 
\end{proof}
\end{lemma}
\begin{proposition} \label{prop:p3ch14.17}
If Y is E-complete, then $\pi_{r}(Y)$ is an R-module. More generally, $\left[X,Y\right]_{r}$ is an R-module for any X.

\begin{proof} 
    Let $m \in  S$; then m gives a morphism $Y \to Y$, which must be an E-equivalence, since the induced map $E_{\ast}(Y) \to E_{\ast}(Y)$ is multiplication by m, which is an invertible element of $\pi_{0}(E)$. So in $\left[Y,Y\right]^E_{0}$ the morphism $m$ has an inverse. Therefore the canonical map
     $$
      \phi\colon  Z \to  \left[Y,Y\right]^E_{0} 
    $$ 
    extends to give 
    $$
      \phi\colon  R \to  \left[Y,Y\right]^E_{0} .
    $$ 
So R acts on $\left[X,Y\right]^E_{\ast}$ for any X. If Y is E-complete, we have $\left[X,Y\right]^E_{\ast}=\left[X,Y\right]_{\ast}$.
\end{proof}
\end{proposition}

\end{document}
